Let There Be Light: \\ Early Observations of the Normal Type Ia Supernova \abc\ \\Show No Evidence for a Dark Period

### 2017-07-27 doc/ms.tex
Remove unnecessary notes to myself or questions for co-authors from the text
Add subsection to text describing different obs of young SNe Ia.

\subsection{SN-Companion collision}

@@

Recently, \citet{2017arXiv170608990H} showed that the early light curve of SN\,2017cbv has a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5 d after explosion. \citeauthor{2017arXiv170608990H} find that the bump can be explained via the combination of ejecta-companion interaction and the normal evolution of a type Ia SN. A challenge for this model is that it significantly overpredicts the UV brightness of the SN compared to what is observed. It is argued in \citet{2017arXiv170608990H} that the shock resulting from the companion collision may not be a blackbody, which could reconcile the model with the observed UV photometry. Qualitatively, \abc\ and SN\,2017cbv exhibit similar characteristics: both feature strong \ion{C}{2} absorption in their early spectra and a bump in their early light curves. Below, we argue for circumstellar interaction and strong $^{56}$Ni mixing as a possible explanation for \abc, and indeed \citet{2017arXiv170608990H} consider these possibilities for SN\,2017cbv as well. While there are arguments in favor of and against each of these possibilities, we believe that the early behavior of SN\,2017cbv and \abc\ reflect a common physical origin.
\amiller{should this paragraph be in the conclusions?}

@@

\amiller{need to mention velocities}

@@

@@

\textbf{Does anyone know of any theoretical studies that specifically predict incomplete burning and strong Ni mixing?}

>>>>

\subsection{SN-Companion collision}
\label{sec:companion}

@@

@@

@@

The proliferation of high-cadence, time-domain surveys has led to several SNe Ia being discovered within $\lesssim$2 d of first light in the past $\sim$decade. Observations probing the early evolution of these SNe allows us to place unique constraints on their progenitor systems and the corresponding explosion physics. This has revealed diversity in the earliest epochs after explosion and that commonly used SNe Ia templates do not match observations (e.g., \citealt{2012ApJ...744...38F}).

In \S\ref{sec:lc_energy} we compared our early observations of \abc\ to SN\,2011fe, which has the most comprehensive observations of the young SNe Ia sample. Given its normal spectroscopic and photometric evolution, SN\,2011fe has been adopted as a standard for the early evolution of SNe Ia in many studies. While a detailed quantitative analysis is beyond the scope of this study, a qualitative examination of very young SNe Ia that otherwise exhibit normal spectra and evolution at and post-peak\footnote{This definition excludes iPTF\,14atg, which was shown to be subluminous with SN\,2002es-like spectra \citep{2015Natur.521..328C}.} reveals considerable diversity. In other words, at early times SN\,2011fe may not be the norm.

For SN\,2011fe the initial rise is well described by a $t^2$ power law, the $(B - V)_0$ colors evolve from the red to the blue, and the \ion{C}{2} present in the initial spectra is weak \citep{2011Natur.480..344N,2016ApJ...820...67Z,2012ApJ...752L..26P}. In contrast, \abc\ exhibits a near linear rise in flux, the $(B - V)_0$ colors are blue and roughly constant, and the \ion{C}{2} absorption is strong. Examining just these 3 qualitative features, SN\,2009ig is well matched to SN\,2011fe \citep{2012ApJ...744...38F}, while SN\,2013dy \citep{2013ApJ...778L..15Z}, SN\,2017cbv \citep{2017arXiv170608990H}, and \abc\ all bear a striking resemblance. SN\,2012cg, on the other hand, appears to be intermediate to these two groups with weak C II and a relatively shallow early rise, like SN\,2011fe, but blue $(B - V)_0$ colors, like \abc\ \citep{2012ApJ...756L...7S,2016ApJ...820...92M}. That these early observations cannot be easily separated into two distinct groups suggests that it is unlikely that a single physical mechanism drives the diversity of SNe Ia at early times.  \amiller{Not sure what to say about 14J - colors are difficult to measure, and ASASSN-14lp no \ion{C}{2} measurement and no discussion of colors}.

In the case of SN\,2012cg and SN\,2017cbv it has been argued that the early blue optical colors are indicative of interaction between the SN ejecta and a binary companion \citep{2016ApJ...820...92M,2017arXiv170608990H}. SN\,2017cbv is particularly remarkable in that the observations presented in \citet{2017arXiv170608990H} show a clearly resolved bump in the $U$, $B$, and $g'$ bands in the $\sim$5 d after explosion. In \citeauthor{2017arXiv170608990H} it is found that the bump can be explained via the combination of ejecta-companion interaction and the normal evolution of a SN Ia. A challenge for this model, similar to \abc\ (see \S\ref{sec:companion}), is that it significantly overpredicts the UV brightness of the SN compared to what is observed. Indeed, in the case of SNe\,2012cg, 2017cbv, and \abc\ the UV - optical colors are significantly redder than those observed in iPTF\,14atg. It is argued in \citet{2017arXiv170608990H} that several model assumptions, including: (i) ideal blackbody emission, (ii) a constant opacity, (iii) a simple power-law density profile for the ejecta, and (iv) spherical symmetry, may be incorrect, which could reconcile the discrepancy with the UV observations. Above, we argued for circumstellar interaction and strong $^{56}$Ni mixing as a possible explanation for \abc, and indeed \citet{2017arXiv170608990H} consider these possibilities for SN\,2017cbv as well. Seperately, several arguments against companion interaction for SN\,2012cg are presented in \citet{2016arXiv161007601S}.

Ultimately, there are arguments in favor of and against each of the possibilties to explain the early emission from SNe Ia. Moving forward, more detailed models and simulations are needed to properly explain the observed diversity. No matter the correct explanation for the early behavior of SNe\,2013dy, 2017cbv, and \abc, the strong similarities between these events suggests they reflect a common physical origin.

@@
